---
title: "Guardener"
author: "Christiaan Pauw and Alex Howard"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(Guardener)
library(tidyverse)
```

# Get access token

You need to have a username and password. For the defaults, Uuse usethis::edit_r_environ() to edit the R environment. These value are be retrived with Sys.getenv("shinyGuardianUN") and Sys.getenv("shinyGuardianPW")

```{r}
#ATL <- Glogin(un = Sys.getenv("shinyGuardianUN"), pw = Sys.getenv("shinyGuardianPW"))
#ATL <- Glogin(un = "StandardRegistry", pw = "test")
#ATL$role
#ATL$did
#ATL$username
#AT <- ATL$accessToken # only the accestoken
dropbase <- gsub(":3838/HGICP-ShinyUI/", ":3000/", Sys.getenv("shinyGaurdianURL"))
AT <- Glogin(un = Sys.getenv("shinyGuardianUN"), 
              pw = Sys.getenv("shinyGuardianPW"), 
              baseurl = dropbase)
AT <- AT$accessToken

```

# Get list of policies 

If the role is Standards Regsitry (or installer?), the use can request a policy list (of tibble when returndf = TRUE )

```{r}
dfPolicies <- GgetPolicies(AT, 
                           returndf = TRUE, 
                           baseurl = dropbase)
dfPolicies2 <- GgetPolicies(AT, 
                            baseurl = dropbase, 
                            returndf = TRUE)

#dfPoliciesDrop <- Guardener::GgetPolicies(AT2, baseurl = "165.232.86.237:3000")
```


# Get an individual policy

```{r}
policy <- GgetPolicy(AT, 
                     policyId = dfPolicies$id[[1]], 
                     baseurl = dropbase, 
                     returndf = TRUE)
```
Information about the block are inside the $config column

Inspect the config:

```{r}
dfConfig <- GgetPolicyConfig(accessToken = AT,  
                             policyId = dfPolicies$id[[1]], 
                             baseurl = dropbase, ) %>% 
  unnest(cols = c(children)) %>% 
   unnest(cols = c(children))
```


# Get blocks from policy

Do all of the above in one step

```{r}
blocks <- GgetPolicyBlocks(accessToken = AT, 
                           policyId = dfPolicies$id,
                           baseurl = dropbase, )
```

Relevant blocks for action are typically of type "requestVcDocumentBlock"

```{r}
blocks %>% filter(blockType == "requestVcDocumentBlock")
```
# Get schemas associated with block

```{r}
blocks[1, c(3,8)]
#Schema_requestVcDocumentBlock <- GgetSchemas(AT, schemaId = unlist(blocks[1, c(8)]), returndf = TRUE)
dfSchemas <- GgetSchemas(AT, baseurl = dropbase,  returndf = TRUE) # "/schema/{schemaId}" gives a 500 so get everything and filter
dfMSchemas <- dfSchemas %>% 
  filter(name == "Monitoring Report (MR)") %>% 
  GmakeSchemaTemplate()
```


